
%-------------------------
% Resume in Latex
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{palatino}
\usepackage{anyfontsize}

\hypersetup{hidelinks}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\newcommand{\normalFont}[1]{\fontsize{9.5pt}{11pt}{\selectfont{#1}}}
\newcommand{\largeFont}[1]{\fontsize{11pt}{11pt}{\selectfont{#1}}}
\newcommand{\LargeFont}[1]{\fontsize{12.5pt}{13pt}{\selectfont{#1}}}

% Sections formatting
\titleformat{\section}{
  \fontsize{13pt}{13pt}\selectfont\bfseries\raggedright
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
      \small\textbf{#1}{: #2 \vspace{-4pt}}
    }
  }

  \newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
      {\vspace{-2pt}}
    }
  }

  % Professional Summary
  \newcommand{\resumeSummary}[1]{
    \normalFont{#1}\par\vspace{-5pt}
  }
  \newcommand{\resumeSubheading}[5]{
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \largeFont{\textbf{#1}} | \normalFont{#3} & \small{#4} \\
      {\normalFont{Stack: } #5} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
  }

  \newcommand{\educationSubheading}[4]{
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \largeFont{\textbf{#1}} & \small{#4} \\
      {\small #3} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
  }


  \newcommand{\skillItem}[2]{
    \item {
      \normalFont{\textbf{#1}{: #2 \vspace{-5pt}}}
    }}

  \renewcommand{\labelitemii}{$\circ$}

  \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
  \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
  \newcommand{\resumeItemListStart}{\begin{itemize}}
  \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{4pt}}

  %-------------------------------------------
  %%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Oscar Castillejo}} \\
  \normalFont{\href[pdfnewwindow=true]{https://www.linkedin.com/in/oscar-castillejo/}{Linkedin: https://www.linkedin.com/in/oscar-castillejo/}} & \normalFont{\href{mailto:oscar.castillejo.sa@gmail.com}{Email: oscar.castillejo.sa@gmail.com}}\\
  \normalFont{\href[pdfnewwindow=true]{https://github.com/oacs}{Github: https://github.com/oacs}} & \normalFont{Mobile: +1-647-615-3226} \\
\end{tabular*}\vspace{-5pt}

%-----------SUMMARY-----------------
\section{Cover Letter}
\resumeSummary{Dear Hiring Manager,\\ \smallskip
I am thrilled to apply for the Senior Engineer II position at Catawiki. As a seasoned software engineer with a passion for delivering impactful and innovative solutions, I believe I have the skills and experience necessary to excel in this role and contribute to the company's success. \smallskip

Throughout my career, I have honed my expertise in the design, implementation, and deployment of backend services, with a focus on ensuring high availability, low latency, and consistency. I have worked closely with cross-functional teams, leveraging my strong collaboration skills to achieve common goals and deliver exceptional results. \smallskip

My deep knowledge of Node.js and ability to effectively communicate technical information to both technical and non-technical audiences have proven to be valuable assets in my previous role. I have a hands-on approach to my work and am always eager to take on new challenges and learn new technologies. \smallskip

In addition to my technical expertise, I am also a team player who thrives in fast-paced and dynamic environments. I am committed to creating a positive and inclusive work culture, and I bring a strong sense of ownership and responsibility to everything I do. \smallskip

I am confident that my skills and experience, combined with my passion for software engineering, make me an excellent fit for the Senior Engineer II role at Catawiki. I am excited about the opportunity to bring my expertise to your team and help the company achieve its goals. \smallskip

Thank you for considering my application. I look forward to the opportunity to further discuss my qualifications and enthusiasm for this role. \smallskip

Sincerely, \smallskip
Oscar Castillejo}
\end{document}
